Cosmological Evidences of Dark Matter through the CMB

### 2018-12-23 paper/main.tex
introduction

\section{Introduction}
-\citep{WayneHu} brief thermal history of the universe and how to get to the cmb and what is it?\\
-practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
which info can we get from the cmb: Big bang, maater and energy content of the universe---dark matter is a big part of the matter content it influenced the spectrum  of the CMB ---- so it played a role.\\
-structure of the paper \\

@@

\section{CMB theo analysis}
\begin{itemize}
\item hydrodynamics \citep{huLectureNotesCMB2008}
page 14 eq 49 to page 17 eq 71\\
skip doppler effect
\item gravito acoustic oscillations page 19 up to eq 82 , justify briefly constant potential in page 20
% if stress perturbations are negligible compared with density perturbations ( δp ≪ δρ ) then the potential will remain constant in periods where the background equation of state p/ρ is constant
\item page 20 and 21 up to eq92 important comment 
%The consequence is that overdense regions where Ψ is negative (potential wells) are cold spots in the effective temperature.
\item baryonic effect
\end{itemize}
hydrodinamics

>>>>

\section{Introduction}
Many astronomical and cosmological observations suggest that there is a missing form of matter that interacts gravitationally. 
Therefore, scientists have proposed the existence of a new form of matter that does not interact electromagnetically but gravitationally: Dark Matter.
Neverthless the fundamental nature of Dark Matter is not well understood, there are strong evidences for the existence of Dark Matter. 
One of the most important evidence of the existance of Dark Matter comes from the analysis of the Cosmic Microwave Background.

Since Dark Matter does not interact electromagnetically, its existence has been animatedly discussed.

-\citep{WayneHu} brief thermal history of the universe and how to get to the cmb and what is it?\\
-practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
which info can we get from the cmb: Big bang, maater and energy content of the universe---dark matter is a big part of the matter content it influenced the spectrum  of the CMB ---- so it played a role.\\
-structure of the paper \\

@@

\section{CMB theo analysis}
\begin{itemize}
\item hydrodynamics \citep{huLectureNotesCMB2008}
page 14 eq 49 to page 17 eq 71\\
skip doppler effect
\item gravito acoustic oscillations page 19 up to eq 82 , justify briefly constant potential in page 20
% if stress perturbations are negligible compared with density perturbations ( δp ≪ δρ ) then the potential will remain constant in periods where the background equation of state p/ρ is constant
\item page 20 and 21 up to eq92 important comment 
%The consequence is that overdense regions where Ψ is negative (potential wells) are cold spots in the effective temperature.
\item baryonic effect
\end{itemize}

\section{Comments on the results and plots of the CMB spectrum}
